Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-06-21 Manuscript.Rmd
sig. statement

Corresponding author: Claudio Toro-Serey (ctoro@bu.edu)

@@

>>>>

Corresponding authors: Claudio Toro-Serey (ctoro@bu.edu) & Joseph T. McGuire (jtmcg@bu.edu)

@@

## Significance Statement

  Much attention has been given to evaluating the apparent neural overlap of various psychological domains in medial prefrontal (mPFC) and posterior cingulate cortices, but recent descriptive analyses of individualized human functional topography suggest a breaking point from group-averaging to examine this issue. Here we show that canonical default network in these regions can be subdivided at the individual level using spectral partitioning, and quantify the heterogeneity of this functional topography across many individuals for the first time. We find that the intrinsic organization of mPFC is particularly variable across individuals, but consistent within individuals over time. This work extends the notion that affirming the neural overlap of distinct behaviors in this area should be done at the individual level.
